\Huge \bf \sc Design and implementation of sensor fusion and control for an autonomous quadrotor

### 2013-07-29 latex/paper/paper.tex

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Santiago Paternain}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
spaternain@gmail.com}
\and
\IEEEauthorblockN{Rodrigo Rosa}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
rodrigorosa.LG@gmail.com}
\and
\IEEEauthorblockN{Mat\'ias Tailani\'an}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
matias@tailanian.com}
\and
\IEEEauthorblockN{Rafael Canetti}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
canetti@fing.edu.uy}
}

@@

\begin{figure}[h!]
%\vspace{-.8cm}
	\centering
	\hspace{10pt}\includegraphics[width=.8\columnwidth]{./pics_paper/diagrama_general.png}
	\caption{\textbf{General diagram.}}
	\label{fig:diagrama_tio}
\end{figure}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Santiago Paternain}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
spaternain@gmail.com}
\and
\IEEEauthorblockN{Mat\'ias Tailani\'an}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
matias@tailanian.com}
\and
\IEEEauthorblockN{Rodrigo Rosa}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
rodrigorosa.lg@gmail.com}
\and
\IEEEauthorblockN{Rafael Canetti}
\IEEEauthorblockA{Facultad de Ingenier\'ia\\
Universidad de la Rep\'ublica\\
Montevideo, Uruguay\\
canetti@fing.edu.uy}
}

@@

\begin{figure}[h!]
\vspace{-.3cm}
	\centering
	\includegraphics[width=.8\columnwidth]{./pics_paper/diagrama_general.png}
	\caption{\textbf{General diagram.}}
	\label{fig:diagrama_tio}
\end{figure}
